Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece

### 2024-08-31 article/article.Rmd
Commit 2024-08-31 14:11

```{r relative-month-occurrences, echo=FALSE, fig.cap="Seasonal variability of the number of CE events in Thessaloniki for the period 1994 -- 2023 normalized to the maximum occurring in June, in the form of a box and whisker plot. The monthly values have also been normalized to the relative abundance of valid GHI observations. The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles, the thick horizontal line and the diamond symbol represent the median and the mean values, respectively. The vertical lines (whiskers) extend between the maximum and minimum monthly values."}
knitr::include_graphics("../images/clim-CE-month-norm-MAX-median-N-MW-1.png")
```

@@

```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Seasonal variability of the number of ECE events in Thessaloniki for the period 1994 -- 2023 normalized to the maximum occurring in March, in the form of a box and whisker plot. The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles. The thick horizontal line and the diamond symbol represent the median and the mean values, respectively. The vertical lines (whiskers) extend between the maximum and minimum monthly values."}
knitr::include_graphics("../images/clim-ECE-month-norm-MAX-median-N-2.png")
```

>>>>

```{r relative-month-occurrences, echo=FALSE, fig.cap="Seasonal variability of the number of CE events relative to the corresponding number of GHI measurements in Thessaloniki for the period 1994 -- 2023, in the form of a box and whisker plot. The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles, the thick horizontal line and the diamond symbol represent the median and the mean values, respectively. The vertical lines (whiskers) extend between the maximum and minimum monthly values."}
knitr::include_graphics("../images/P-CE-climatology-normlz-1.png")
```

<!--
```{r relative-month-occurrence, echo=FALSE, fig.cap="Seasonal variability of the number of CE events in Thessaloniki for the period 1994 -- 2023 normalized to the maximum occurring in June, in the form of a box and whisker plot. The monthly values have also been normalized to the relative abundance of valid GHI observations. The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles, the thick horizontal line and the diamond symbol represent the median and the mean values, respectively. The vertical lines (whiskers) extend between the maximum and minimum monthly values."}
knitr::include_graphics("../images/clim-CE-month-norm-MAX-median-N-MW-1.png")
```
-->

@@

```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Seasonal variability of the number of ECE events relative to the the corresponding number of GHI measurements in Thessaloniki for the period 1994 -- 2023, in the form of a box and whisker plot. The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles. The thick horizontal line and the diamond symbol represent the median and the mean values, respectively. The vertical lines (whiskers) extend between the maximum and minimum monthly values."}
knitr::include_graphics("../images/P-ECE-climatology-normlz-1.png")
```

<!--
```{r relative-month-occurancies-ECEs, echo=FALSE, fig.cap="Seasonal variability of the number of ECE events in Thessaloniki for the period 1994 -- 2023 normalized to the maximum occurring in March, in the form of a box and whisker plot. The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles. The thick horizontal line and the diamond symbol represent the median and the mean values, respectively. The vertical lines (whiskers) extend between the maximum and minimum monthly values."}
knitr::include_graphics("../images/clim-ECE-month-norm-MAX-median-N-2.png")
```
-->

### 2024-08-31 article/article.tex
Commit 2024-08-31 14:11

{\centering \includegraphics[width=1\linewidth]{../images/clim-CE-month-norm-MAX-median-N-MW-1}

@@

\caption{Seasonal variability of the number of CE events in Thessaloniki for the period 1994 -- 2023 normalized to the maximum occurring in June, in the form of a box and whisker plot. The monthly values have also been normalized to the relative abundance of valid GHI observations. The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles, the thick horizontal line and the diamond symbol represent the median and the mean values, respectively. The vertical lines (whiskers) extend between the maximum and minimum monthly values.}\label{fig:relative-month-occurrences}
\end{figure}

@@

{\centering \includegraphics[width=1\linewidth]{../images/clim-ECE-month-norm-MAX-median-N-2}

@@

\caption{Seasonal variability of the number of ECE events in Thessaloniki for the period 1994 -- 2023 normalized to the maximum occurring in March, in the form of a box and whisker plot. The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles. The thick horizontal line and the diamond symbol represent the median and the mean values, respectively. The vertical lines (whiskers) extend between the maximum and minimum monthly values.}\label{fig:relative-month-occurancies-ECE}
\end{figure}

>>>>

{\centering \includegraphics[width=1\linewidth]{../images/P-CE-climatology-normlz-1}

@@

\caption{Seasonal variability of the number of CE events relative to the corresponding number of GHI measurements in Thessaloniki for the period 1994 -- 2023, in the form of a box and whisker plot. The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles, the thick horizontal line and the diamond symbol represent the median and the mean values, respectively. The vertical lines (whiskers) extend between the maximum and minimum monthly values.}\label{fig:relative-month-occurrences}
\end{figure}

@@

{\centering \includegraphics[width=1\linewidth]{../images/P-ECE-climatology-normlz-1}

@@

\caption{Seasonal variability of the number of ECE events relative to the the corresponding number of GHI measurements in Thessaloniki for the period 1994 -- 2023, in the form of a box and whisker plot. The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles. The thick horizontal line and the diamond symbol represent the median and the mean values, respectively. The vertical lines (whiskers) extend between the maximum and minimum monthly values.}\label{fig:relative-month-occurancies-ECE}
\end{figure}
